Faceted Bar Charts

### 2016-05-12 articles/articles.Rmd
scatter plot

- Doing Data Science Right — Your Most Common Questions Answered. [[Review](http://firstround.com/review/doing-data-science-right-your-most-common-questions-answered/?imm_mid=0e29cf&cmp=em-data-na-na-newsltr_20160413)]
- Principles of good data analytics. [[blog](http://www.gregreda.com/2014/03/23/principles-of-good-data-analysis/)] 
- Why I Ditched My Fitbit and What This Means for Analytics. [[Data Science Central](http://www.datasciencecentral.com/profiles/blogs/why-i-ditched-my-fitbit-and-what-this-means-for-analytics)]
- Know the Difference between Customer Service and Customer Experience. [[Harvard Business Review](https://hbr.org/sponsored/2016/03/know-the-difference-between-customer-service-and-customer-experience?utm_source=twitter&utm_medium=social&utm_campaign=harvardbiz)]
- Two articles about saying no to p-values. [[R-bloggers](http://www.r-bloggers.com/after-150-years-the-asa-says-no-to-p-values/)][[R-bloggers](http://www.r-bloggers.com/its-not-the-p-values-fault-reflections-on-the-recent-asa-statement-relevant-r-resources/)]
- The 9 Best Marketing And Sales Analytics You Should Know About.[[Data Science Central](http://www.datasciencecentral.com/profiles/blogs/the-9-best-marketing-and-sales-analytics-you-should-know-about)]
- Cohort analysis. [[Youtube](https://www.youtube.com/watch?v=NyhVdGmnh0I)]
- Ted Talk : How to use data to make a hit TV show. [[Ted](http://www.ted.com/talks/sebastian_wernicke_how_to_use_data_to_make_a_hit_tv_show?utm_campaign=social&utm_medium=referral&utm_source=facebook.com&utm_content=talk&utm_term=technology)]

>>>>

- 6 Best Practices for implementing In-store Personalization in 2015. [[beaconstac](http://blog.beaconstac.com/2015/07/6-best-practices-for-implementing-in-store-personalization-in-2015/)]
    - Activating purchases: Say, Laura purchased a lemon yellow shirt at your retail store outlet located in New York. Now, a week later, you can send out an offer (via email and through a mobile app push notification) on a brown trouser that’ll go along with the shirt. The offer can be redeemed on your online store or a physical outlet.
    - Pushing shoppers forward in the buying path: Say the same customer, Laura, actually went on to browse handbags online after she received the email offer. As soon she walks into your physical retail store, you can send a  notification through her mobile app, asking if she wishes to touch and feel the handbags that she browsed online.
- How Big Data is changing e-commerce for good [[Future of Commerce](http://www.the-future-of-commerce.com/2014/12/15/how-big-data-is-changing-e-commerce-for-good/)]
    - The top three things that retailers needs to know: how effective their pricing is, when shoppers are most active and what items they buy together (promoting products that shoppers often buy together can boost your average order value and help products move more quickly). 
- Do data scientists need to be domain experts to deliver good analytics? [[Data Science Central](http://www.datasciencecentral.com/profiles/blogs/do-data-scientists-need-to-be-domain-experts-to-deliver-good)]
    - Often, good data scientists become subject experts just by playing with the data and asking questions to domain experts about the data anomalies. Through their questioning they will cross-pollinate the subject matter experts so the team as a whole is stronger.
    - Machine learning brings a fresh perspective that leads to new insights and no prior domain knowledge can potentially be advantageous, especially in overcoming long standing domain bias.
- Using Machine Learning to Predict Customer Behaviour [[Data Science Central](http://www.datasciencecentral.com/profiles/blogs/using-machine-learning-to-predict-customer-behaviour)]
    - Used with Complaints Management, Customer Upsell and Customer Retention. Questions include How to anticipate and manage the dissatisfaction of the customers?', 'How to sell more and better to existing customers?' and 'How to keep the most profitable customers at an appropriate cost?'
    - Action: You identify a target behaviour, in our case, it is a specific customer action, like filing a complaint/not filing a complaint, accepting or rejecting an upsell offer, cancelling / not cancelling a service. Then perform supervised learning
- Doing Data Science Right — Your Most Common Questions Answered. [[Review](http://firstround.com/review/doing-data-science-right-your-most-common-questions-answered/?imm_mid=0e29cf&cmp=em-data-na-na-newsltr_20160413)]
- Principles of good data analytics. [[blog](http://www.gregreda.com/2014/03/23/principles-of-good-data-analysis/)] 
- Why I Ditched My Fitbit and What This Means for Analytics. [[Data Science Central](http://www.datasciencecentral.com/profiles/blogs/why-i-ditched-my-fitbit-and-what-this-means-for-analytics)]
- Know the Difference between Customer Service and Customer Experience. [[Harvard Business Review](https://hbr.org/sponsored/2016/03/know-the-difference-between-customer-service-and-customer-experience?utm_source=twitter&utm_medium=social&utm_campaign=harvardbiz)]
- Two articles about saying no to p-values. [[R-bloggers](http://www.r-bloggers.com/after-150-years-the-asa-says-no-to-p-values/)][[R-bloggers](http://www.r-bloggers.com/its-not-the-p-values-fault-reflections-on-the-recent-asa-statement-relevant-r-resources/)]
- The 9 Best Marketing And Sales Analytics You Should Know About.[[Data Science Central](http://www.datasciencecentral.com/profiles/blogs/the-9-best-marketing-and-sales-analytics-you-should-know-about)]
- Cohort analysis. [[Youtube](https://www.youtube.com/watch?v=NyhVdGmnh0I)]
- Ted Talk : How to use data to make a hit TV show. [[Ted](http://www.ted.com/talks/sebastian_wernicke_how_to_use_data_to_make_a_hit_tv_show?utm_campaign=social&utm_medium=referral&utm_source=facebook.com&utm_content=talk&utm_term=technology)]

### 2016-05-12 articles/avoid_pie_charts/avoid_pie_charts.Rmd
scatter plot

---
title: "Collection of Visualization"
date: "`r Sys.Date()`"
author: "Ming-Yu Liu"
output:
  rmdformats::readthedown:
    highlight: haddock
---

Articles related to producing informative visualization.

# Avoiding Pie Charts

Date: 2016.3.16

The purpose of a pie chart is to show the relationship of parts out of a whole. With that being said they can still be really bad at the one thing they're ostensibly designed to do. Consider the following pie chart from the [Wall Street Journal](http://www.wsj.com/articles/what-data-scientists-do-all-day-at-work-1457921541) article on What Data Scientists Do All Day at Work.

<img src = "/Users/ethen/Business-Analytics/visualization/avoid_pie_charts/data_scientist.png" width = "400" height = "800" >

@@

library(scales)
library(ggplot2)
library(ggthemes)
library(data.table)
setwd("/Users/ethen/Business-Analytics/visualization/avoid_pie_charts")
d <- fread("pie.txt")
d <- melt( d, id.vars = "Task", 
		   variable.name = "Hours", value.name = "Percentage" )
head(d)

@@

## Plots

@@

**Sources:** source code can be obtained [here](https://github.com/ethen8181/Business-Analytics/blob/master/visualization/avoid_pie_charts/pie.R).

## Reference

1. Worst Chart In The World: http://www.businessinsider.com/pie-charts-are-the-worst-2013-6
2. How to replace a pie chart: http://varianceexplained.org/r/improving-pie-chart/
3. Take the Pies out of Pi Day: http://rud.is/b/2016/03/14/spinning-cycles-in-box-4-to-take-the-pies-out-of-pi-day/

# Next Chart

>>>>

---
title: "Faceted Bar Charts"
date: "`r Sys.Date()`"
author: "Ming-Yu Liu"
output:
  rmdformats::readthedown:
    highlight: haddock
---

> Source code can be obtained [here](https://github.com/ethen8181/Business-Analytics/blob/master/articles/avoid_pie_charts/avoid_pie_charts.R)

The purpose of a pie chart is to show the relationship of parts out of a whole. With that being said they can still be really bad at the one thing they're ostensibly designed to do. Consider the following pie chart from the Wall Street Journal article on What Data Scientists Do All Day at Work.

<img src = "/Users/ethen/Business-Analytics/articles/avoid_pie_charts/data_scientist.png" width = "400" height = "800" >

@@

library(scales)
library(ggplot2)
library(ggthemes)
library(data.table)
setwd("/Users/ethen/Business-Analytics/articles/avoid_pie_charts")
d <- fread("avoid_pie_charts_data.txt")
d <- melt( d, id.vars = "Task", 
		   variable.name = "Hours", value.name = "Percentage" )
head(d)

@@

@@

**Reference**

- [Worst Chart In The World](http://www.businessinsider.com/pie-charts-are-the-worst-2013-6)
- [How to replace a pie chart](http://varianceexplained.org/r/improving-pie-chart/)
- [Take the Pies out of Pi Day](http://rud.is/b/2016/03/14/spinning-cycles-in-box-4-to-take-the-pies-out-of-pi-day/)
